\documentclass[12pt]{article}

\usepackage{multicol}
\usepackage{geometry}
\usepackage{fontspec}
\usepackage{anyfontsize}
\usepackage{xcolor}
\usepackage{setspace}
\usepackage{nopageno}
\usepackage{tabularx}
\usepackage{fancyhdr}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}

\definecolor{mainGray}{gray}{.5}
\definecolor{hrulegray}{gray}{.5}

\geometry{margin=1cm, footskip=4.35004pt, headheight=14.49998pt}
\setsansfont{GlacialIndifference-Regular.otf}
\setlength{\parindent}{0em}
\setlength{\parskip}{0em}
\setlength{\columnsep}{.05\textwidth}

\renewcommand{\headrulewidth}{0pt}
\pagestyle{fancy}
\cfoot{}
% \rfoot{%\color{mainGray}\footnotesize\sffamily Made with \rmfamily\LaTeX.}

\newcommand{\sechead}[1]{{
\fontspec{GlacialIndifference-Regular.otf}\bfseries \footnotesize
\MakeUppercase{#1}
}}

\newcommand{\job}[4]{{
\vspace{6pt}
\fontspec{GlacialIndifference-Bold.otf}#1\\
\fontspec{GlacialIndifference-Regular.otf} \footnotesize
#2 | #3
\footnotesize \fontspec{GlacialIndifference-Regular.otf}\begin{itemize}[leftmargin=.17in,itemsep=0in]
#4
\end{itemize}
}}

\newcommand{\skill}[2]{{
\small {\fontspec{GlacialIndifference-Bold.otf}#1} | \fontspec{GlacialIndifference-Regular.otf}#2
\vspace{6pt}
}}

\newcommand{\course}[1]{{\fontspec{GlacialIndifference-Regular.otf}{#1}}}

\hyphenpenalty=10000
\exhyphenpenalty=10000
\raggedright

\begin{document}
\sffamily

\begin{multicols}{2}
{\fontspec{GlacialIndifference-Regular.otf} \Huge Carter Parks}\\[6pt]

{%\color{mainGray}
Full Stack Web Developer\\
}
\vspace{14pt}
{%\color{hrulegray}\hrule
}

\columnbreak

\begin{flushright}
{\small \fontspec{GlacialIndifference-Regular.otf}\href{https://carterparks.org}{carterparks.org}\\
\href{https://github.com/CarterParks}{github.com/CarterParks}\\
435\,\textbullet\,225\,\textbullet\,1558 | \href{mailto:software@carterparks.org}{software@carterparks.org}\\
Logan, UT\\
}
\end{flushright}

\end{multicols}

\sechead{Skills}\\[6pt]
\hrule\\[6pt]

\skill{VueJS, HTML, CSS}{
Frontend web development at ControlByWeb
}\\

\skill{Linux}{
Used as a development platform for coursework and employment, and as a personal desktop.
Comfortable in commandline and server environments.
}\\

\skill{Git}{
Comfortable with version control best practices.
}\\

\skill{TypeScript, NodeJS, ExpressJS, MongoDB}{
Backend web development for employment at Symliv LLC.
}\\

\skill{Python, Django}{
Coursework and backend web development for Logan Small Business Development Center.
Language of choice for personal projects.
}\\

\skill{Java}{
Coursework to learn and develop algorithms.
}\\

\skill{C, CUDA, OpenMP}{
Coursework in Numerical Analysis and High Performance Computing contexts.
}\\

\skill{LaTeX}{
Coursework document production in various mathematics contexts.
}\\

\vspace{14pt}
\sechead{Experience}\\[6pt]
\hrule\\[6pt]

\job{ControlByWeb}{Software Engineer}{MAY 2023 - PRESENT}{
\item Development of management platform for internet enabled industrial hardware
\item Frontend development with VueJS
\item Backend development with Laravel
\item Management of AWS based infrastructure
}

\job{Symliv LLC}{Software Developer}{JUN 2021 - MAY 2023}{
\item Developed customer facing access control for vacation rentals
\item Built backend and frontend on a cloud-based MERN stack
\item Implemented image generation and cloud storage
\item Administered DNS
}

\job{Logan Small Business Development Center}{Developer and IT Consultant}{APR 2020 - JUN 2021}{
\item Provided support for IT related concerns new companies had
\item Used the SCORM API to track user learning
\item Developed e-commerce websites
}

% \job{Utah State University}{Logan, UT}{Custodian}{MAR 2019 - APR 2020}{
% Responsibilities included maintenance and janitorial duties. Required working under a deadline and following rigorous protocols.}\\
%
% \job{American Burgers}{Tooele, UT}{Cashier}{JUN 2018 - DEC 2018}{
% Responsibilities included handling money, interacting with customers, preparing and packaging food, and training new hires, along with various situational demands. Required working in a team and under pressure.}\\

\vspace{14pt}
\sechead{Education}\\[6pt]
\hrule\\[6pt]

\job{Utah State University}{Computer Science BS, Minor in Mathematics}{JAN 2019 - MAY 2023}{
\item Gave experience working with groups, solving complicated problems efficiently, and rapidly getting up to speed on new topics.
\item Learned the tenets of good software and algorithm design, with a grounding in Computer Science theory
\item Mathematics Minor gave a foundation to interface with complex ideas and topics related to Computer Science
}

%\job{Grantsville High School}{High School Diploma}{AUG 2014 - MAY 2018}{
%\item 4 Years Grantsville High School Tennis Team
%\item 4 Years Grantsville High School Speech and Debate Team.
%\item 2 Years member of the Grantsville High School Chapter National Honors Society.
%\item Sterling Scholar Award for Speech/Forensics
%}

%\job{Internship at the University of Idaho}{Moscow, ID}{Chemical Engineering Dept.}{JUN 2015 - JUL 2015}{
%Assisted in computer modeling of metabolic networks.
%}

% \sechead{Qualities}\\
% 
% \skill{Passion}{I enjoy every aspect of computers, and love to learn about them. If there is something that I don't know well enough, I am more than willing to learn it in my free time, and I can learn it quickly.}\\
% 
% \skill{Teamwork}{I enjoy working with a group, and love seeing a plan well executed. My past employment has relied heavily on each team member functioning as part of a whole.}\\
% 
% \skill{Organization}{I can follow plans and procedures, and work well under management. I am a result-oriented person, focused on honesty and accomplishing goals.}\\

\vfill
{\color{mainGray}\footnotesize \fontspec{GlacialIndifference-Regular.otf}XeLaTeX source for this document can be found at \href{https://github.com/CarterParks/resume}{github.com/CarterParks/resume}}

\end{document}
